---
title: "R Notebook"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## 2. Read Data
We start by importing the Data

```{r}
library(arules)
supermarket <- read.transactions("C:/Users/user/Desktop/Supermarket_Sales_Dataset II.csv", sep = ",")
```
```{r}
head(supermarket)
```

```{r}
tail(supermarket)
```

#summary
```{r}
summary(supermarket)
```
```{r}
class(supermarket)
```
```{r}
str(supermarket)
```
```{r}
inspect(supermarket[1:5])
```
# Exploring the frequency of some articles.
# View transactions ranging from 10 to 12 and performing 
# some operation in percentage terms of the total transactions 


```{r}
itemFrequency(supermarket[, 8:12],type = "absolute")
round(itemFrequency(supermarket[, 8:12],type = "relative")*100,2)
```

# plot the frequency of items
```{r}
itemFrequencyPlot(supermarket, topN = 10,col="darkgreen")
itemFrequencyPlot(supermarket, support = 0.1,col="darkred")
```
# Building a model based on association rules using the apriori function

# We use Min Support as 0.001 and confidence as 0.8

```{r}
rules <- apriori (supermarket, parameter = list(supp = 0.001, conf = 0.8))
rules
```
# Building a apriori model with Min Support as 0.002 and confidence as 0.8
```{r}
rules2 <- apriori (supermarket, parameter = list(supp = 0.002, conf = 0.8)) 
rules2
```

# Building apriori model with Min Support as 0.002 and confidence as 0.6
```{r}
rules3 <- apriori (supermarket, parameter = list(supp = 0.001, conf = 0.6)) 
rules3
```
```{r}
summary(rules)
```
# Observing rules built in our model i.e. first 5 model rules
```{r}
inspect(rules[1:2])
```

# Order these rules by a criteria such as the level of confidence
# then looking at the first five rules.
```{r}
rules<-sort(rules, by="confidence", decreasing=TRUE)
inspect(rules[1:2])
```
# 1. Determine items that customers who previously bought eggs might buy 
```{r}
milk<- subset(rules, subset = lhs %pin% "eggs")

# Then order by confidence
milk <-sort(milk, by="confidence", decreasing=TRUE)
inspect(milk[1:5])
```

# 2. Determine items that customers who previously bought avocado might buy 
```{r}
avocado <- subset(rules, subset = lhs %pin% "turkey")
```
# Then order by confidence
```{r}
avocado <-sort(avocado, by="confidence", decreasing=TRUE)
inspect(turkey[1:3])
```

# 3. Determine which items customers bought before purchasing chocolate
```{r}
chocolate <- subset(rules, subset = rhs %pin% "chocolate")

# Then order by confidence
chocolate <-sort(chocolate, by="confidence", decreasing=TRUE)
inspect(chocolate[1:2])
```